Results

### 2020-01-19 analysis/02_analysis.Rmd
Modernize tidyverse syntax and use newer stan functions

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  scale_dag() +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

@@

```{r tbl-descriptive-statistics, results="asis", warning=FALSE}
vars_to_summarize <- tribble(
  ~variable, ~clean_name,
  "donate_likely", "Likelihood of donation",
  "donate_likely_bin", "Likelihood of donation (binary)",
  "amount_donate", "Amount hypothetically donated ($)",
  "gender", "Gender",
  "age", "Age",
  "income", "Income",
  "education", "Education",
  "religiosity", "Frequency of attending religious services",
  "ideology", "Political views",
  "political_knowledge", "Frequency of following public affairs",
  "give_charity", "Frequency of charitable donations",
  "volunteer", "Volunteered in past 12 months",
  "favor_humanitarian", "Prior favorability towards humanitarian NGOs",
  "favor_humanitarian_bin", "Prior favorability towards humanitarian NGOs (binary)",
  "favor_human_rights", "Prior favorability towards human rights NGOs",
  "favor_human_rights_bin", "Prior favorability towards human rights NGOs (binary)",
  "favor_development", "Prior favorability towards development NGOs",
  "favor_development_bin", "Prior favorability towards development NGOs (binary)",
  "check2", "Attention check 2"
)

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  gather(variable, value) %>% 
  group_by(variable) %>% 
  nest() %>% 
  mutate(N = data %>% map_int(~ nrow(.)),
         summary = map2(.x = data, .y = variable, ~ md_summary_row(.x$value, .y, results))) %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  mutate(variable = factor(variable, levels = vars_to_summarize$variable, ordered = TRUE)) %>% 
  arrange(variable) %>% 
  select(-data, -variable) %>% 
  unnest(summary) %>% 
  select(Variable = clean_name, N, ` ` = spark, Details = summary)

@@

```{r tbl-results-conditions, results="asis"}
conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
                                group_by(results, crackdown, issue) %>% nest(),
                                group_by(results, crackdown) %>% nest(),
                                results %>% nest()) %>% 
  arrange(crackdown, issue, funding) %>% 
  mutate(summary = data %>%
           map(~ summarize(., pct_likely = table(donate_likely_bin)[["Likely"]] /
                             length(donate_likely_bin),
                           mean_donation = mean(amount_donate, na.rm = TRUE),
                           sd_donation = sd(amount_donate, na.rm = TRUE),
                           N = nrow(.)))) %>% 
  unnest(summary) %>% select(-data)

@@

    return(list(
      n_total_1 = df_counts$total[1],
      n_total_2 = df_counts$total[2],
      n_likely_1 = df_counts$n[1],
      n_likely_2 = df_counts$n[2]
    ))
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data_counts %>% map(~ {
    sampling(donate_likely(), data = .x, control = list(max_treedepth = 15),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

tbl_likely_1 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE}
tbl_likely_2 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2a~ and H~3a~` = title_clean, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE}
tbl_likely_3 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            funs(percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  select(`H~2a~ and H~3a~ (nested)` = Frame,
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

@@

```{r run-amount-models, results="hide", cache=TRUE}
# Sample from the compiled model
all_models_amount_run <- all_models %>% 
  # Simplify data for sending to Stan
  mutate(stan_data = df %>% map(~ {
    select(.x, amount = amount_donate, group = crackdown)
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data %>% map(~ {
    sampling(amount_donated_best(), data = compose_data(.x),
             chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

tbl_amount_1 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE}
tbl_amount_2 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE}
tbl_amount_3 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), funs(as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`H~2b~ and H~3b~ (nested)` = Frame,
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

>>>>

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

@@

```{r tbl-descriptive-statistics, results="asis"}
vars_to_summarize <- tribble(
  ~variable_name, ~clean_name,
  "donate_likely", "Likelihood of donation",
  "donate_likely_bin", "Likelihood of donation (binary)",
  "amount_donate", "Amount hypothetically donated ($)",
  "gender", "Gender",
  "age", "Age",
  "income", "Income",
  "education", "Education",
  "religiosity", "Frequency of attending religious services",
  "ideology", "Political views",
  "political_knowledge", "Frequency of following public affairs",
  "give_charity", "Frequency of charitable donations",
  "volunteer", "Volunteered in past 12 months",
  "favor_humanitarian", "Prior favorability towards humanitarian NGOs",
  "favor_humanitarian_bin", "Prior favorability towards humanitarian NGOs (binary)",
  "favor_human_rights", "Prior favorability towards human rights NGOs",
  "favor_human_rights_bin", "Prior favorability towards human rights NGOs (binary)",
  "favor_development", "Prior favorability towards development NGOs",
  "favor_development_bin", "Prior favorability towards development NGOs (binary)",
  "check2", "Attention check 2"
)

results_summary_stats <- results %>% 
  select(one_of(vars_to_summarize$variable_name)) %>% 
  summarise_all(~list(.)) %>% 
  pivot_longer(everything(), names_to = "variable_name", values_to = "value") %>% 
  mutate(N = value %>% map_int(~ length(na.omit(.))),
         summary = map2(.x = value, .y = variable_name, ~ md_summary_row(.x, .y))) %>% 
  left_join(vars_to_summarize, by = "variable_name") %>% 
  mutate(variable_name = factor(variable_name, 
                                levels = vars_to_summarize$variable_name, 
                                ordered = TRUE)) %>% 
  arrange(variable_name) %>% 
  select(-value, -variable_name) %>% 
  unnest(summary) %>% 
  select(Variable = clean_name, N, ` ` = spark, Details = summary)

@@

```{r tbl-results-conditions, warning=FALSE, results="asis"}
conditions_summary <- bind_rows(group_by(results, crackdown, issue, funding) %>% nest(),
                                group_by(results, crackdown, issue) %>% nest(),
                                group_by(results, crackdown) %>% nest(),
                                results %>% nest(data = everything())) %>% 
  arrange(crackdown, issue, funding) %>% 
  mutate(summary = data %>%
           map(~ summarize(., pct_likely = table(donate_likely_bin)[["Likely"]] /
                             length(donate_likely_bin),
                           mean_donation = mean(amount_donate, na.rm = TRUE),
                           sd_donation = sd(amount_donate, na.rm = TRUE),
                           N = nrow(.)))) %>% 
  unnest(summary) %>% select(-data) %>% ungroup()

@@

    return(list(
      n_total_1 = df_counts$total[1],
      n_total_2 = df_counts$total[2],
      n_likely_1 = df_counts$n[1],
      n_likely_2 = df_counts$n[2]
    ))
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data_counts %>% map(~ {
    donate_likely(n_total_1 = .x$n_total_1, n_total_2 = .x$n_total_2,
                  n_likely_1 = .x$n_likely_1, n_likely_2 = .x$n_likely_2,
                  control = list(max_treedepth = 15),
                  chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

tbl_likely_1 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            list(~percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  select(Frame = title, `% likely~Treatment~` = theta_2, `% likely~Control~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-likely-diffs-level2, warning=FALSE, message=FALSE}
tbl_likely_2 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            list(~percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>% 
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2a~ and H~3a~` = title_clean, 
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-likely-diffs-level3, warning=FALSE, message=FALSE}
tbl_likely_3 <- tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate_at(vars(theta_1, theta_2, theta_diff, pct_change), 
            list(~percent_format(accuracy = 0.1)(.))) %>% 
  mutate(p.diff.not0 = as.character(round(p.diff.not0, 2))) %>%
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  select(`H~2a~ and H~3a~ (nested)` = Frame,
         `% likely~Crackdown~` = theta_2, `% likely~No\\ crackdown~` = theta_1,
         `$\\Delta$` = theta_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

@@

```{r run-amount-models, results="hide", cache=TRUE, warning=FALSE}
# Sample from the compiled model
all_models_amount_run <- all_models %>% 
  # Simplify data for sending to Stan
  mutate(stan_data = df %>% map(~ {
    select(.x, amount = amount_donate, group = crackdown)
  })) %>% 
  # Run the actual model on the simplified data
  mutate(model = stan_data %>% map(~ {
    amount_donated_best(df = .x, chains = CHAINS, iter = ITER, 
                        warmup = WARMUP, seed = BAYES_SEED)
  }))

@@

tbl_amount_1 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 1") %>%
  mutate(title = recode(title, 
                        Crackdown = "Crackdown − No crackdown",
                        Issue = "*Humanitarian assistance − Human rights*",
                        Funding = "*Private − Government funding*")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), list(~as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`Frame` = title, `Amount~Treatment~` = mu_2, `Amount~Control~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-amount-diffs-level2, warning=FALSE, message=FALSE}
tbl_amount_2 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 2") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title_clean = case_when(
    title_clean %in% c("Human rights", "Humanitarian assistance") ~ paste(title_clean, "issues"),
    title_clean %in% c("Government", "Private") ~ paste(title_clean, "funding")
  )) %>% 
  mutate(title_clean = factor(title_clean, 
                              levels = c("Human rights issues", 
                                         "Humanitarian assistance issues", 
                                         "Government funding", "Private funding"))) %>% 
  arrange(title_clean) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), list(~as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  mutate(title_clean = as.character(title_clean)) %>% 
  select(`H~2b~ and H~3b~` = title_clean, `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```

```{r tbl-amount-diffs-level3, warning=FALSE, message=FALSE}
tbl_amount_3 <- tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  filter(category == "Level 3") %>%
  mutate(title_clean = str_remove(title, " \\| Crackdown")) %>% 
  separate(title_clean, c("Issue", "Funding"), sep = " \\| ") %>% 
  mutate(Issue = factor(Issue, levels = c("Human rights", "Humanitarian assistance")),
         Funding = factor(Funding, levels = c("Government", "Private"))) %>% 
  arrange(Issue, Funding) %>% 
  mutate(Frame = paste0(Issue, " issues, ", Funding, " funding")) %>% 
  mutate_at(vars(mu_1, mu_2, mu_diff, p.diff.not0), list(~as.character(round(., 2)))) %>% 
  mutate(pct_change = percent_format(accuracy = 0.1)(pct_change)) %>%
  select(`H~2b~ and H~3b~ (nested)` = Frame,
         `Amount~Crackdown~` = mu_2, `Amount~No\\ crackdown~` = mu_1,
         `$\\Delta$` = mu_diff, `$\\%\\Delta$` = pct_change, 
         `$p(\\Delta \\neq 0)$` = p.diff.not0)
```
